Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-01-03 template.tex
fixed a key typo
another small typo
fixed a typo in template
big new commit, with new progress on simplifying the final envelope

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Analytic Askaryan Signals}

@@

\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:

@@

\item The overal analytic signal, $s_a(t)$, is

@@

\item Let $x(t) * y(t)$ represent the convolution of two functions $x(t)$ and $y(t)$.  Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.  $\mathcal{E}_{x * y}(t)$, $r_a(t)$, and $s_a(t)$ are related by

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)

@@

This result can be further simplified.

>>>>

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

\title{Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals}

@@

\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:

@@

\item The overall analytic signal, $s_a(t)$, is

@@

\item Let $x(t) * y(t)$ represent the convolution of two functions $x(t)$ and $y(t)$.  Let the envelope of the convolution be $\mathcal{E}_{x * y}(t)$.  $\mathcal{E}_{x * y}(t)$, $x_a(t)$, and $y_a(t)$ are related by

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \label{eq:Re} \\
r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0) \label{eq:Im}

@@

This result can be further simplified.  There are several intermediate steps that aid in the simplification.  First, note that $Q(z_0)$ is related to the \textit{Voigt functions} $U(x,t)$ and $V(x,t)$:
U(x,t) &= j V(x,t) = \frac{\pi}{4 t} e^{z^2} \erfc(z) \\
z &= \frac{1-jx}{2\sqrt{t}} \label{eq:z_def}
Note that $t$ and $x$ are real parameters, and that the Voigt functions are also real.  Let $z = \frac{1}{2}z_0$. The parameters are connected to $z_0$ by the following:
\Re \lbrace z_0 \rbrace &= \frac{1}{\sqrt{t}} \\
\gamma ' &= \frac{1}{\sqrt{t}} \\
\Im \lbrace z_0 \rbrace &= -\frac{x}{\sqrt{t}} \\
x &= \frac{2\pi f_0'}{\gamma'} = \frac{2\pi f_0}{\gamma} \label{eq:x}
It is significant that $x$ is the ratio of the detector parameters.  Thus, $Q(z_0)$ may be written in terms of $U$ and $V$:
Q(z_0) = \frac{2}{\gamma'\sqrt{\pi}}\left(U + j V\right)
Equation \ref{eq:Im} simplifies:
\boxed{r_a(t) * \Im\lbrace s_a(t)\rbrace = \frac{R_0 s(t)}{\gamma} \left(U + j V \right)} \label{eq:int_1}
To simplify Eq. \ref{eq:Re}, we need the derivative of $Q(z_0)$ with respect to $z_0$:
\frac{dQ}{dz_0} = \frac{1}{2}z_0 Q(z_0) - \frac{1}{\sqrt{\pi}} \label{eq:derivative}
Combining Eqs. \ref{eq:Re}, \ref{eq:z_def}, and \ref{eq:derivative}, we find
r_a(t) * \Re\lbrace s_a(t)\rbrace = E_0 \sigma_t^2 r_a \left(1 - \frac{z_0}{\gamma'}\left(U + j V \right)\right)
Using the definitions of $z_0$, $\gamma'$, and Eq. \ref{eq:x}, we find
\boxed{r_a(t) * \Re\lbrace s_a(t)\rbrace = E_0 \sigma_t^2 r_a \left(1 - \left(1 + j x \right)\left(U + j V \right)\right)} \label{eq:int_2}
There are useful limits for Voigt functions:
\lim_{t\to 0} U(x,t) &= \frac{1}{1+x^2} \\
\lim_{t\to 0} V(x,t) &= \frac{x}{1+x^2}
Taking this limit for Eqs. \ref{eq:int_1} and \ref{eq:int_2}, we find, to first-order in $1/\gamma'$, 
r_a(t) * \Im\lbrace s_a(t)\rbrace &\approx \frac{R_0s(t)}{\gamma} \\
r_a(t) * \Re\lbrace s_a(t)\rbrace &\approx 0
\item 
Using Eq. \ref{eq:awesome}, we find
\boxed{\mathcal{E}_{r * s}(t) = \frac{R_0|s(t)|}{2\gamma}}
This result appears to have (1) the right units, (2) the right limits, and (3) the right symmetry.  However, the \textit{width} of this theoretical envelope is limited by the width of $s(t)$.  The limit that the Voigt parameter $t \to 0$ implies that $\gamma' \gg 1$.  This is not necessarily a good limit for realistic detectors.
